Slight Positive Correlation Between Gendered and Racialized Police Strip Searches in the Toronto Municipal, 2020-2021

### 2024-01-25 outputs/paper/paper.qmd
refine graphs

#create a scatterplot to show each observation in the dataset, comparing the total reasons to racial identitiy found in each strip search
#colour the points based on the perceived race of the captive
#code for geom_point() referenced from https://github.com/TDonofrio62/Shooting-Occurrences-in-Toronto/blob/main/Shooting_Occurrences/outputs/paper/Shooting_Occurrences.Rmd
cleaned_search_reasons_data |>
  group_by(total_reasons, items_found, race) |>
  count() |>
  rename(count = n) |>
  ggplot(aes(x = total_reasons, y = count, colour = race, size = count)) +
  geom_point(alpha = 0.5) +
  theme_bw() +
  theme(legend.key.size = unit(0.5, 'cm'))
  labs(x = "Total Reasons for Strip Searching",
       y = "Count",
       color = "Race"
       ) +
  scale_fill_viridis_d(option="cividis")

@@

```{r}
#| echo: false
#| message: false
#| label: fig-reasons-gender
#| fig-cap: Relationship Between Reasons for Strip Search and Gender in Toronto, 2020-2021

cleaned_search_reasons_data |>
  group_by(total_reasons, items_found, gender) |>
  count() |>
  rename(count = n) |>
  ggplot(aes(x = total_reasons, y = count, colour = gender, size = count)) +
  geom_point(alpha = 0.5) +
  theme_bw() +
  theme(legend.key.size = unit(0.5, 'cm'))
  labs(x = "Total Reasons for Strip Searching",
       y = "Count",
       color = "Gender"
       ) +
  scale_fill_viridis_d(option="cividis")

>>>>

#create a scatterplot to show each observation in the dataset, comparing the total reasons to racial identitiy found in each strip search
#colour the points based on the perceived race of the captive
#code for geom_point() referenced from https://github.com/TDonofrio62/Shooting-Occurrences-in-Toronto/blob/main/Shooting_Occurrences/outputs/paper/Shooting_Occurrences.Rmd
cleaned_search_reasons_data |>
  group_by(total_reasons, race) |>
  count() |>
  rename(count = n) |>
  ggplot(aes(x = total_reasons, y = count, colour = race, size = count)) +
  geom_point(alpha = 0.5) +
  theme_bw() +
  theme(legend.key.size = unit(0.5, 'cm'))
  labs(x = "Total Reasons for Strip Searching",
       y = "Count",
       color = "Race"
       ) +
  scale_fill_viridis_d(option="cividis")

@@

```{r}
#| echo: false
#| message: false
#| results: hide
#| label: fig-reasons-gender
#| fig-cap: Relationship Between Reasons for Strip Search and Gender in Toronto, 2020-2021

cleaned_search_reasons_data |>
  group_by(total_reasons, gender) |>
  count() |>
  rename(count = n) |>
  ggplot(aes(x = total_reasons, y = count, colour = gender, size = count)) +
  geom_point(alpha = 0.5) +
  theme_bw() +
  theme(legend.key.size = unit(0.5, 'cm'))
  labs(x = "Total Reasons for Strip Searching",
       y = "Count",
       color = "Gender"
       ) +
  scale_fill_viridis_d(option="cividis")
